---
title: "Problem Set 2"
author: "Colby Pastel"
date: "2024-01-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.align = 'center',
  message = FALSE,
  warning = FALSE
)
```

1. [enter url here]

2. See the corrected code chunck below. A total of 8 changes were made.

```{r}
library(tidyverse)

# open my data
gspace = read_csv('greenspace_data_share.csv') # missing quotation marks (1)

# summarize average urban greenspace by region
tab1 = # Renamed "table" to "tabl" to prevent confusion with tidyverse command (2)
  gspace |>
    group_by(Major_Geo_Region) |> # added a pipe (3)
      summarise(
        obs = n(), # added a comma (4)
        avg = mean(annual_avg_2020), # added an underscore (5)
        weighted_avg = mean(annual_weight_avg_2020) # changed a space to an underscore (6)
      )

# output as table
knitr::kable(tab1, digits = 1) # added "knitr::" (7), changed "gspace" to "tab1" (8)
```

3. The greenspace data covers **1,038** urban areas.

```{r}
dim(gspace)
#str(gspace)
#unique(gspace$City)
```

4. The mean average greenspace for urban areas in 2021 was 0.280 and the 
average greenspace ranged from 0.045 to 0.630. The median and mean average 
greenspace were identical, 0.280.   

```{r}
summary(gspace$annual_avg_2021, digits = 2)
```

5.a. The number of urban areas which Scored High or above for greenspace in 
2015 was **66**.

```{r}
gspace |>
  filter(
    indicator_2015 == 'High' | 
    indicator_2015 == 'Very High'
  ) |>
  count()
```

5.b. The number of urban areas which Scored Exceptionally Low at any point in 
the years covered was **240**.

```{r}
gspace |>
  filter(
    indicator_2010 == 'Exceptionally Low' | 
    indicator_2015 == 'Exceptionally Low'| 
    indicator_2020 == 'Exceptionally Low' |
    indicator_2021 == 'Exceptionally Low',
    ) |>
  count()
```

5.c. The number of urban areas with arid climates that became greener from 
2010 to 2020 was **225**.

```{r}
gspace |>
  filter(
    Climate_region == 'Arid',
    annual_weight_avg_2020 > annual_weight_avg_2010
  ) |>
  count()
```

6. **128** urban areas became less green from 2010 to 2021. These changes were 
concentrated in Europe and Asia, and urban areas with climates besides arid and 
polar.

```{r}
gspace |>
  filter(
    annual_avg_2010 > annual_avg_2021
  ) |>
  count()

tab2 =
  gspace |>
    filter(
      annual_avg_2010 > annual_avg_2021
    )
  
tab2 |>
  count(Major_Geo_Region, name = 'Freq')

tab2 |>
  count(Climate_region, name = 'Freq')
```
\newpage

7. See histogram below.

```{r}
tab3 =
  gspace |> 
    summarize(
      gspace_2010 = annual_avg_2010,
      gspace_2021 = annual_avg_2021,
      Diff = annual_avg_2021 - annual_avg_2010
    )

hist(tab3$Diff, 
     main = 'Histogram (2010 - 2021)', 
     xlab = 'Change in Greenspace')
```
\newpage

8. See scatter plot below.

```{r}
plot(gspace_2021 ~ gspace_2010, tab3, 
     main = 'Population Weighted Greenspace', 
     xlab = 'Avg 2010',
     ylab = 'Avg 2021')
```
\newpage

Bonus Opportunity: See scatter plot below.

```{r}
plot(gspace_2021 ~ gspace_2010, tab3, 
     col = ifelse(Diff > 0, 'darkgreen', 'black'), 
     main = 'Population Weighted Greeenspace', 
     xlab = 'Avg 2010', ylab = 'Avg 2021')
abline(0,1, col = 'red')
```
